Title

### 2023-06-08 main.tex
correcciones y citas brasil

\tbnote{versión muy preliminar de la intro, para ir teniendo algo escrito de una vez. }\\

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open systems, 
which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. 
Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles
defined by the following equations:
\begin{align*}
\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\\
\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}}, \\
\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.
\end{align*}

@@

\begin{theorem}
\label{theorem2}
Consider a 1PR circuit of $N$ qubits
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is} |a^j\rangle + e^{-is} |b^j\rangle + |c^j\rangle
\end{align*}
with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
c^j|c^j \rangle = 1$.
\end{theorem}
\textbf{Proof:} 
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

@@

Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is} |\tilde{b}^{j}\rangle + e^{is} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle
\end{align}
where we defined
\begin{align*}
|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align*}
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

Finally, after having applied the rotation, the circuit applies gate $A$, 
so that the result is given by:
\begin{eqnarray}
U|j\rangle = ARB|j\rangle = e^{-is} A |\tilde{a}^j\rangle + e^{is} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is} |a^j\rangle + e^{is} |b^j\rangle + |c^j\rangle,
\end{eqnarray}
where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
states that satisfy $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ because $A$ is unitary. $\blacksquare$  \\
 $\;$ \\

This theorem implies that when starting from the state $|0\rangle$ 
or any other initial state, the only possible curves of states that can be 
created using a 1PR circuit are of the following form:
\begin{equation}
|\eta(p)\rangle = |c\rangle + e^{is}|a\rangle + e^{-is} |b\rangle,
\label{eq:curve-states}
\end{equation}
with conditions defined by the equations: 
\begin{equation}
\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1,  \quad
\langle a |b\rangle =
\langle a |c\rangle =
\langle b |c\rangle = 0
% , |b\rangle, |c\rangle \; \text{orthogonal states},
%  \text{and} \; a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
\label{eq:conditions-vecs}
\end{equation}
where $s = s(p)$ is a function of $p$. 
% \cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
% que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
% la notacion. } \tbnote{Va, concuerdo, listo}
% \cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
% luego tunearlo (todo este parrafo). Avisame cuando quede eso!} \tbnote{Ya}

@@

$$
RB|0\rangle =\sqrt{\langle a | a \rangle} e^{is} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
$$
Finally, applying the defined operator $A$ to this state yields the desired result.

@@

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given this condition \cpnote{which?}, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is} |a\rangle + e^{-is}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ \cpnote{redundante, refierete mejor a la ecuacion anterior, a la 24 pues. Ahora, también creo qeu la pedendencia
con $p$ no está clara del lado derecho. Quizpa si se escribe $s(p)$ en vez de 
$s$ es mejor, pero piensale tambien . }.

@@

\begin{itemize}
\item \textbf{Bit flip map:} 
\cpnote{Aca solo usas dos niveles, pero el caso general requiere 2 qubits. Ahora, si solo 
se requiere un qubit, pues está chido pero toca decirlo. Quizá dejarlo como un ultimo ejemplo. 
Toca citar acá tambien el trabajo de los brasileños... a ver si lo encuentro, Andrea 
Valdez me va a pasar la cita. De hecho pordemos leer el articulo para inspiracion y citar}
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$\cpnote{Que tal si lo dejamos como $\sin s= \sqrt{p}$? Si estas de 
acuerdo igual cambia los siguientes}.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.

\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Then, taking the $\beta_j$ to be real,
the curve of states needed to create on the ancilla qubits is
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right),
\end{align*}
with $s = \arcsin(\sqrt{3p/4})$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.
\cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}

\item \textbf{Parabolic dynamical map:} Finally, we define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |0\rangle + \dfrac{1}{2} \sqrt{1-p^2} |1\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |2\rangle +  \dfrac{1}{2}(1+p) |3\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|0\rangle + \dfrac{1}{2} |3\rangle \right) + e^{is} \left( \dfrac{i}{4}|0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle - \dfrac{i}{4} |3\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle + \dfrac{i}{4} |3\rangle \right),
\end{align*}
with $s = \arcsin(p)$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.
\end{itemize}

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|, |b|, |c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
This way, since the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps 
that can be implemented with a 1PR circuit in \fref{fig:curves2}.
These maps where constructed with the additional condition
of the map passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta}|0\rangle$ with $\theta$ an arbitrary
real number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $e^{i \theta}|0\rangle$, which
corresponds with the identity channel.

\cpnote{Esta parte está desordenada. Porque parece qeu das el procedimiento 
en los 3 putnos de arriba y leugo que siempre no, qu evalta algo. Trata de iterar el paso 3 
estos dos parrafos para que tengan un flujo mas chido. }
To fulfill this additional condition,  we restrict the first row of
$V$ writen as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.

>>>>

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open systems, 
which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
{\color{purple} For example, this has been done using optical arrangements
to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles
defined by the following equations:
\begin{align}
\label{eq:angle}
\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\\
\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}}, \\
\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.
\end{align}

@@

\begin{theorem}
\label{theorem2}
Consider a 1PR circuit of $N$ qubits parametrized by $p$
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
\end{align*}
with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
c^j|c^j \rangle = 1$.
\end{theorem}
\textbf{Proof:} 
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

@@

Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
and a phase $e^{is(p)}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is(p)} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is(p)} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is(p)} |\tilde{b}^{j}\rangle + e^{is(p)} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle
\end{align}
where we defined
\begin{align*}
|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align*}
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

Finally, after having applied the rotation, the circuit applies gate $A$, 
so that the result is given by:
\begin{eqnarray}
U|j\rangle = ARB|j\rangle = e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
\end{eqnarray}
where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
states that satisfy $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ because $A$ is unitary. $\blacksquare$  \\
 $\;$ \\

This theorem implies that when starting from the state $|0\rangle$ 
or any other initial state, the only possible curves of states that can be 
created using a 1PR circuit are of the following form:
\begin{equation}
|\eta(p)\rangle = |c\rangle + e^{is(p)}|a\rangle + e^{-is(p)} |b\rangle,
\label{eq:curve-states}
\end{equation}
with conditions defined by the equations: 
\begin{equation}
\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1,  \quad
\langle a |b\rangle =
\langle a |c\rangle =
\langle b |c\rangle = 0.
\label{eq:conditions-vecs}
\end{equation}
% \cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
% que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
% la notacion. } \tbnote{Va, concuerdo, listo}
% \cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
% luego tunearlo (todo este parrafo). Avisame cuando quede eso!} \tbnote{Ya}

@@

$$
RB|0\rangle =\sqrt{\langle a | a \rangle} e^{is(p)} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is(p)} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
$$
Finally, applying the defined operator $A$ to this state yields the desired result.

@@

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
{\color{red}
where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$}
 \cpnote{redundante, refierete mejor a la ecuacion anterior, a la 24 pues. Ahora, también creo qeu la pedendencia
con $p$ no está clara del lado derecho.}

\tbnote{Va, algo así (quitar lo 
rojo, dejar lo morado):}

{\color{purple} where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.}

\cpnote{
 Quizpa si se escribe $s(p)$ en vez de 
$s$ es mejor, pero piensale tambien . } 
\tbnote{Es cierto, mejor, ya lo puse}.\\

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-3p/4)$, $|\beta_1(p)|^2 = |\beta_2(p)|^2 = |\beta_3(p)|^2 = p/4$.
Then, taking the $\beta_j$ to be real,
thi curve of states is
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.
\cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}
\tbnote{Va, listo.}

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits is:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

\item \textbf{Bit flip map:} 
\cpnote{Aca solo usas dos niveles, pero el caso general requiere 2 qubits. Ahora, si solo 
se requiere un qubit, pues está chido pero toca decirlo. Quizá dejarlo como un ultimo ejemplo. 
Toca citar acá tambien el trabajo de los brasileños... a ver si lo encuentro, Andrea 
Valdez me va a pasar la cita. De hecho pordemos leer el articulo para inspiracion y citar} \tbnote{Va, puse explícitamente lo de que sólo se usa un qubit más abajo} \tbnote{Tambien puse la cita del trabajo brasileño}
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |00\rangle +\sqrt{p} |01\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |00\rangle - \dfrac{i}{2} |01\rangle \right) + e^{-is} \left( \frac{1}{2} |00\rangle + \frac{i}{2} |01\rangle \right),
\end{align*}
with $\sin s= \sqrt{p}$\cpnote{Que tal si lo dejamos como $\sin s= \sqrt{p}$? Si estas de 
acuerdo igual cambia los siguientes} \tbnote{Va, ya los cambié}.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
{\color{purple} Note that in this case we actually only need one ancilla qubit
since the state $|\beta(p)\rangle$ is only two dimensional.}

The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.
{\color{purple}
For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
using an optical arrangement, and  it was indeed done 
by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).}

\end{itemize}

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|, |b|, |c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
This way, given that the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}.

{\color{purple} However, since a Pauli dynamical map should begin at the
identity channel, we need to add the condition that $|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$, with
$\theta$ an arbitrary real number. 
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $e^{i \theta}|0\rangle$, which
corresponds with the identity channel.

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.}
\end{itemize}

Following this procedure for random
angles and unitary matrices $V$, 
we plot four Pauli dynamical maps  selected at random
that can be implemented with a 1PR circuit in \fref{fig:curves2}.

{\color{red}
These maps where constructed with the additional condition
of the map passing through the identity channel.
To do that, we ensure that the vectors also satisfy
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta}|0\rangle$ with $\theta$ an arbitrary
real number.
This way, when $s = 0$ in \eref{eq:vec}, the constructed state
is $e^{i \theta}|0\rangle$, which
corresponds with the identity channel.
